Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-01-13 eswc-2012/phdsymp.tex
snip
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@86 43ef1190-90fd-4dd7-a769-d0121f02b80e

This part of the thesis addresses problems of query optimization in a
federated regime.

@@

The above relies on data and queries that are in fact
representative of the system as a whole. It is often asserted that it
is not possible to create a ``one-size-fits-all'' benchmark (see
e.g. \cite{Schmidt:2011:FBS:2063016.2063054}) to cover all aspects of
an application. While that may be true in the general case, I want to
challenge the assumption that the best we can do is to accommodate a
multitude of dimensions and essential challenges in the case of
SPARQL.

>>>>

@@

The above relies on data and queries that are in fact representative
of the system as a whole. It is often asserted that it is not possible
to create a ``one-size-fits-all'' benchmark (see
e.g. \cite{Schmidt:2011:FBS:2063016.2063054}) to cover all aspects of
an application. While that may be true in the general case, I want to
challenge the assumption that the best we can do is testing queries on
a best effort basis in the case of SPARQL.
